Evaluating the evidence of widespread maintenance of functional composition in vertebrate communities

### 2022-04-27 paper/manuscript.Rmd
forrrrmattting

journal: "Ecology Letters"
date: "`r Sys.Date()`"
bibliography: refs.bib
layout: 3p
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output: 
  rticles::arxiv_article:
    keep_tex: true
#  word_document: default
editor_options: 
  markdown: 
    wrap: sentence

@@

### Introduction

@@

### Material and Methods

#### Data

@@

#### Diversity Metrics

@@

#### Null Models

@@

#### Analysis

@@

### Results

@@

### Discussion

@@

#### Evidence of Ecological Processes

@@

<!-- We observed no significant trends within taxa. Even Amphibians, considered highly sensitive to human impact, maintained functional structure through time.  Indicates that we could've looked at any taxonomic subset of the data and gotten the same result. But what does that mean for taxa we left out? We can only make educated guesses based on what we know of the ecology of taxa that were left out - taxa specific papers? -->

#### Potential Methodological Limitations

@@

#### Policy Implications

@@

#### Future Work

@@

### Data Availability

@@

### Acknowledgments

We thank the scientists who contributed to and maintain the biodiversity databases included in this study, including BioTIME, Amphibio, and Elton Traits.
We thank Dr Shane Blowes and Dr Sarah Supp, whose code we adapted for initial data processing of the BioTIME database.
Support for this work was provided by United States Department of Energy through the Computational Sciences Graduate Fellowship (DOE CSGF) under grant number DE-FG02-97ER25308 awarded to K.E.A.N..

### References

>>>>

journal: "Ecology Letters"
date: "`r Sys.Date()`"
bibliography: refs.bib
layout: 3p
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output: 
  rticles::arxiv_article:
    keep_tex: true
#  word_document: default
editor_options: 
  markdown: 
    wrap: sentence
keywords:
  - biodiversity change
  - functional traits
  - global change
  - timeseries

@@

## Significance Statement {.unnumbered}

The globe is in the midst of a biodiversity crisis due to anthropogenic impacts. It is critical to understand how ecological communities are changing in response xxx. Previous broad-scale assessments of biodiversity change through time have focused on metrics of species identity rather than the role species play in the community. Functional trait data offer a powerful opportunity to directly assess changes in community functional composition alongside species-based patterns. Here, we pair vertebrate community timeseries with functional trait data to take a first look at temporal trends in functional composition. We found no evidence of systematic functional loss across communities, with maintenance of all measured aspects

# Introduction

@@

# Material and Methods

## Data

@@

## Diversity Metrics

@@

## Null Models

@@

## Analysis

@@

# Results

@@

# Discussion

@@

## Evidence of Ecological Processes

@@

## Potential Methodological Limitations

@@

## Policy Implications

@@

## Future Work

@@

# Data Availability

@@

# Acknowledgments

We thank the scientists who contributed to and maintain the biodiversity databases included in this study, including BioTIME, Amphibio, and Elton Traits.
We thank Dr Shane Blowes and Dr Sarah Supp, whose code we adapted for initial data processing of the BioTIME database.
Support for this work was provided by U.S. Department of Energy through the Computational Sciences Graduate Fellowship (DE-FG02-97ER25308) awarded to K.E.A.N..

# References
